---
title: "R Notebook"
output: html_notebook
---

## Set directory and libraries

```{r}
directory = 'E:/Documents/fair_shares_ds_projects/FS_P003_Customer_Order_List' #desktop
# directory = 'C:/Users/Robert/Documents/_ds_fairshares/FS_P003_Customer_Order_List' #laptop
setwd(directory)

library(tidyverse)
library(DT)
library(googlesheets4)
library(openxlsx)
library(emoji)
library(emo)
# library(googledrive)

```

## load data file

```{r}
date = '05_18_2022'
week = 'Wk 9'

order_only_list = c('1 No Share - Order Only (even wk)',
                    '1 No Share - Order Only (odd wk)',
                    '1 No Produce - Order Only (even wk)',
                    '1 No Produce - Order Only (odd wk)')

file_name = paste0('Member Pick-up Details-',date,'.csv')
# file_name = 'Member Pick-up Details-06_09_2021.csv'
df_orig = read.csv(paste0(directory,'/farmigo_downloads/',file_name)) |> 
  rename_all(tolower) |> 
  rename(group_name = pickup.site, firstname = first.name, lastname = last.name) |> 
  mutate(id = row_number())
```

## connect to settings sheet

```{r}
r_email = ""
gs4_auth(email = r_email)
# drive_auth(email = r_email)
```

## load settings data

```{r}
sh_shares = range_read('1pEEGA3mawQWmgDtIjJmpBMPws8_-EyEqPtQlucGVlNQ'
                ,sheet = 'shares'
                ,col_types = 'ccccc--'
                ,skip = 1
)

sh_delete = range_read('1pEEGA3mawQWmgDtIjJmpBMPws8_-EyEqPtQlucGVlNQ'
                ,sheet = 'delete'
                ,col_types = 'c'
)

# sh_plants = range_read('1pEEGA3mawQWmgDtIjJmpBMPws8_-EyEqPtQlucGVlNQ'
#                 ,sheet = 'pot_plants'
#                 ,col_types = 'c'
# )
```

## Group Check

Making sure that the Group Names in the CSV file match the Group Names we have in Google Sheets. If not then we need to update the Google Sheet document with the new Group Name. Otherwise keep running code. 

If there are groups here that have "Trial" in them then flag to Sara or Jamie. 

```{r}
group_check = df_orig |> 
  select(group_name) |> 
  distinct() |> 
  mutate(check = ifelse(group_name %in% (sh_shares)$group_name, TRUE, FALSE)) |> 
  filter(check == FALSE)

stopifnot(dim(group_check)[1] == 0)

if (dim(group_check)[1] > 0) {
  group_check
}

```


## Member Count - Start

```{r}
df_orig_sh = df_orig  |>  
  left_join(sh_shares |> #bringing in short group name
          select(group_name, group_name_short) |> 
          distinct()
          , by = c('group_name')
          ) |> 
  mutate(group_name = ifelse(is.na(group_name_short) 
                             | group_name_short == '', group_name, group_name_short)
         ) |>
  select(-group_name_short)

sh_shares_shrt = sh_shares |> 
  mutate(group_name = ifelse(is.na(group_name_short) 
                             | group_name_short == '', group_name, group_name_short)
         ) |>
  select(-group_name_short)

member_start = df_orig_sh |> 
  select(group_name, firstname, lastname) |> 
  distinct() |> 
  group_by(group_name) |> 
  summarise(n_start = n())

member_start

```


## Make data long and separate date to be processed without quantity

```{r}

df_orig_long = df_orig_sh  |> 
  mutate(order = strsplit(as.character(order), ",")) |>
  unnest(order) |> 
  mutate(pickuptime = ifelse(str_detect(order, "Pickup Time"), 2, NA),
         order = trimws(order),
         item_original = order
         ) |> 
  separate(order, into = c('quantity','item'), sep = 'x', extra = "merge") |> 
  mutate(item = ifelse(is.na(item) & !is.na(quantity), quantity, item)
         ,quantity = ifelse(item == quantity, NA, quantity)
         ,group_bool = ifelse(is.na(quantity) & !is.na(item) & !item %in% order_only_list, 1, NA)
         ,rank = ifelse(!is.na(group_bool), group_bool,
                        ifelse(!is.na(pickuptime), pickuptime, 3))
         ,name_long = paste0(lastname,', ',firstname,' [',id,']')
         ) |> 
  select(-group_bool, -pickuptime) |> 
  rbind(df_orig_sh |> #bringing in a new row for each group_name
          select(group_name) |> 
          distinct() |> 
          mutate(firstname = '0'
                 ,lastname = '0'
                 ,quantity = NA
                 ,item = group_name
                 ,id = 0
                 ,item_original = group_name
                 ,rank = -1
                 ,name_long = paste0(lastname,', ',firstname,' [',id,']')
                  )
        ) |> 
    rbind(df_orig_sh |> #bringing in a new row for each member name
          select(group_name, firstname, lastname, id) |> 
          distinct() |> 
          mutate(quantity = NA
                 ,item = paste0(lastname,', ',firstname)
                 ,rank = 0
                 ,item_original = item
                 ,name_long = paste0(lastname,', ',firstname,' [',id,']')
                  ) |> 
          select(group_name, firstname, lastname, quantity, item, id, item_original, rank, name_long)
        ) |> 
    rbind(df_orig_sh |> #bringing in a new spacer row for each member name
          select(group_name, firstname, lastname, id) |> 
          distinct() |> 
          mutate(quantity = NA
                 ,item = NA
                 ,rank = 4
                 ,item_original = NA
                 ,name_long = paste0(lastname,', ',firstname,' [',id,']')
                  ) |> 
          select(group_name, firstname, lastname, quantity, item, id, item_original, rank, name_long)
        ) |> 
  arrange(group_name, lastname, firstname, id, rank) 

df_orig_long

```

## Pickup Times found

```{r}
pickup_time = df_orig_long |> 
  filter(rank == 2) |> 
  group_by(Time = item) |> 
  summarise(count = n()) |> 
  ungroup() |> 
  mutate(val = Time) |> 
  separate(val, into = c('q','time','description'), sep = ' ', extra = "merge") |> 
  arrange(description, time, q) 

pickup_time_counts = pickup_time |> 
  select(Time, count)

pickup_time_counts

df_long_tm = df_orig_long |> 
  left_join(
    df_orig_long |> 
      filter(rank == 2) |> 
      select(id, item) |> 
      distinct() |> 
      left_join(pickup_time |> 
                  select(item = Time, description, time)
                , by = c('item')
      ) |>                                #accounts for if a member accidentally puts in two pickup times
      arrange(id, description, time) |>   # look at first based on description and pickup time
      group_by(id) |> 
      mutate(count = rank(row_number())) |> 
      filter(count == 1) |> 
      rename(time_descr = item) |> 
      select(-count) |> 
      ungroup()
    , by = c('id')
  ) |> 
  mutate(description = ifelse(rank == -1, '.....', description)) |> 
  arrange(group_name, description, time, lastname, firstname, id, rank) 

df_long_tm

df_long_tm |> 
  filter(rank == 2) |> 
  group_by(name_long) |> 
  mutate(count = sum(n())) |> 
  filter(count > 1) |> 
  select(name_long, item, count) |> 
  distinct()
```


## Standard Share

```{r}
# fs_w_stndrd = NA
# fs_t_stndrd = NA
# fsa_stndrd = 'Foster, Bill [?]' ##'Foster, Bill [9]'
# fsb_stndrd = 'Abente, Betsy [?]'
# fsc_w_stndrd = 'Ismaeel, Carrie [?]'
# fsc_t_stndrd = NA
# fsd_stndrd = NA
# fsm_w_stndrd = 'Biundo (staff), Rebecca [?]'
# fsm_t_stndrd = NA
# uca_stndrd = NA
# ucb_stndrd = 'Abente, Betsy [?]'
# ucm_stndrd = NA
# kwa_stndrd = NA
# kwb_stndrd = NA
# kwm_stndrd = NA
# 
# fs_w_keep = NA
# fs_t_keep = NA
# fsa_keep = TRUE
# fsb_keep = TRUE
# fsc_w_keep = TRUE
# fsc_t_keep = NA
# fsd_keep = NA
# fsm_w_keep = TRUE
# fsm_t_keep = NA
# uca_keep = NA
# ucb_keep = TRUE
# ucm_keep = NA
# kwa_keep = NA
# kwb_keep = NA
# kwm_keep = NA

############################################################

#Wednesday
group_a_stndrd = 'Picker, Don Knobbe and Lisa [20]'     #Foster, Bill
group_h_stndrd = 'Johnson, Sara [46]'    #Block, Chantal
group_c_stndrd = 'Coolman, Audrey [69]'
group_m_stndrd = 'Bohn, Michelle [90]'     #Biundo (staff), Rebecca
group_u_stndrd = 'Auffenberg, Carolyn [132]'       #Karch/Slocum, Eric and Lee

#Wednesday
group_a_keep = TRUE
group_h_keep = TRUE
group_c_keep = TRUE
group_m_keep = TRUE
group_u_keep = TRUE

############################################################

# #Thursday
# group_a_stndrd = 'Garrett, Elizabeth/Kelly [32]'
# group_h_stndrd = 'Wippermann, Jennifer [146]'     #Rothgangel, Ella    #Kinman, Tricia 
# group_c_stndrd = 'Gaston, Sarah [7]'               #Kruszynski, Stacy
# group_m_stndrd = 'Cordia, Wendy [81]'                #Karr, Mary
# group_u_stndrd = 'Lampitt, Maggie [121]'             #Arbanas, Michael
# 
# #Thursday
# group_a_keep = TRUE
# group_h_keep = NA
# group_c_keep = TRUE
# group_m_keep = TRUE
# group_u_keep = TRUE

############################################################

# #Friday
# group_a_stndrd = NA
# group_h_stndrd = NA
# group_c_stndrd = NA
# group_m_stndrd = 'Sanftner, Tracy [6]'  #Przyzycki, Lori
# group_u_stndrd = NA
# 
# #Friday
# group_a_keep = NA
# group_h_keep = NA
# group_c_keep = NA
# group_m_keep = TRUE
# group_u_keep = NA

############################################################


food_list_group_name = c('A','H','C','M','U')

# shares = c('Fair Shares Wednesday Pickup', 'Fair Shares Thursday Pickup',
#            'FSA', 'FSB', 'FSC-W', 'FSC-T', 'FSD', 'FSMini-w', 'FSMini-t',
#            'UCA', 'UCB', 'UCM', 'KWA', 'KWB', 'KWM'
#            )
# shares = sh_shares$group_name
# 
# df_stndrds = data.frame(group_name = shares
#                          ,name_long = c(fs_w_stndrd, fs_t_stndrd, 
#                                         fsa_stndrd, fsb_stndrd, 
#                                         fsc_w_stndrd, fsc_t_stndrd, fsd_stndrd, fsm_w_stndrd, fsm_t_stndrd, 
#                                         uca_stndrd, ucb_stndrd, ucm_stndrd, 
#                                         kwa_stndrd, kwb_stndrd, kwm_stndrd
#                                         )
#                          ,keep_remove = c(fs_w_keep, fs_t_keep, 
#                                         fsa_keep, fsb_keep, 
#                                         fsc_w_keep, fsc_t_keep, fsd_keep, fsm_w_keep, fsm_t_keep, 
#                                         uca_keep, ucb_keep, ucm_keep, 
#                                         kwa_keep, kwb_keep, kwm_keep)
#                          )

df_stndrds = data.frame(food_list_group_name
                         , name_long = c(group_a_stndrd, group_h_stndrd, group_c_stndrd
                                         , group_m_stndrd, group_u_stndrd)
                         , keep_remove = c(group_a_keep, group_h_keep, group_c_keep
                                         , group_m_keep, group_u_keep)
                         )

df_stndrds = df_stndrds |> 
  inner_join(sh_shares_shrt |> 
              select(group_name, food_list_group_name)
            , by = c('food_list_group_name')
            ) |> 
  mutate(name_long = as.character(name_long))

df_stndrds_item = df_long_tm |> 
  inner_join(df_stndrds |> 
               filter(!is.na(name_long))
             , by = c('name_long')
             ) |> 
  filter(rank == 3) 
  
df_stndrds_item_grp = df_stndrds_item |> 
  select(food_list_group_name, item) |> 
  distinct()|> 
  left_join(sh_shares_shrt |> 
              select(group_name, food_list_group_name)
            , by = c('food_list_group_name')
            ) |> 
  select(-food_list_group_name) |> 
  mutate(standard_item = 1)

stndrd_customers_all = df_long_tm |> 
  left_join(df_stndrds_item |> 
              select(food_list_group_name, item_original) |> 
              distinct()|> 
              group_by(food_list_group_name) |> 
              mutate(rank_v = rank(row_number()),
                     stndrd_rows= max(rank_v)
                     ) |>
              ungroup() |> 
              left_join(sh_shares_shrt |> 
                           select(group_name, food_list_group_name)
                         , by = c('food_list_group_name')
                         ) |> 
              select( -rank_v, -food_list_group_name)
            , by = c('group_name', 'item_original')
            ) |> 
  filter(rank == 3) |> 
  select(id, name_long, group_name, item_original, stndrd_rows) |> 
  distinct() |> 
  group_by(id) |> 
  mutate(rank_v = sum(ifelse(!is.na(stndrd_rows), 1, 0)),
         customer_rows = max(rank_v),
         rank_n_full = ifelse(!is.na(stndrd_rows), rank(row_number()), 0),
         customer_n_full_rows = max(rank_n_full),
         n_full_rows = sum(ifelse(rank_n_full == 0, 1, 0))
         ) |>
  ungroup() 

stndrd_customers_full_match = stndrd_customers_all |> 
  filter(stndrd_rows == customer_rows & n_full_rows == 0) |> 
  left_join(df_stndrds |> 
              filter(!is.na(name_long))
            , by = c('name_long')
            ) |> 
  mutate(keep_remove = ifelse(is.na(keep_remove), TRUE, keep_remove)) |> 
  select(id, keep_remove) |> 
  distinct() 

stndrd_customers_match_w_extras = stndrd_customers_all |> 
  filter(stndrd_rows == (customer_n_full_rows - n_full_rows) & n_full_rows > 0) |> 
  select(id) |> 
  distinct() |> 
  left_join(stndrd_customers_all |> 
              filter(is.na(stndrd_rows)) |> 
              select(id, item_original)
              , by = c('id')
  ) |> 
  mutate(keep_remove =  TRUE) |> 
  select(id, item_original, keep_remove) |> 
  distinct() 
  

df_long_def = df_long_tm |> #bring in stndrd trading member names
  filter(id %in% (stndrd_customers_full_match |> filter(keep_remove == TRUE))$id
         | id %in% (stndrd_customers_match_w_extras |> filter(keep_remove == TRUE))$id
           ) |> 
  filter(rank <= 2) |> 
  select(-item_original) |> 
  rbind(df_long_tm |>  #bring in stndrd trading item row
          filter(id %in% (stndrd_customers_full_match |> filter(keep_remove == TRUE))$id
                 | id %in% (stndrd_customers_match_w_extras |> filter(keep_remove == TRUE))$id
            ) |> 
          filter(rank >= 3) |> 
          mutate(quantity = NA,
                 item = ifelse(rank == 3, 'STANDARD SHARE ITEMS', item)
                 ) |> 
          select(-item_original) |> 
          distinct()
  ) |> 
  rbind(df_long_tm |>  #bring in all members not in stndrd member list
          select(-item_original) |> 
          filter(!id %in% (stndrd_customers_full_match |> filter(keep_remove == TRUE))$id
                 & !id %in% (stndrd_customers_match_w_extras |> filter(keep_remove == TRUE))$id
                 )
  ) |> 
  rbind(df_long_tm |>  #bring in items that have a stndrd item match but have extra sales
          inner_join(stndrd_customers_match_w_extras |> 
                       select(-keep_remove)
                    , by = c('id','item_original')
                     ) |> 
          select(-item_original) 
  ) |> 
  arrange(group_name, description, time, lastname, firstname, id, rank) |> 
  left_join(df_stndrds_item_grp
            , by = c('item','group_name'))

##location for site total data frame built similar to query above with slight mods
  
df_long_def |> 
  inner_join(stndrd_customers_match_w_extras |> 
             select(-item_original) |> 
             mutate(extras = TRUE) |> 
             distinct() |> 
             rbind(stndrd_customers_full_match |> 
                     mutate(extras = FALSE))
             , by = c('id')
             ) |> 
  select(group_name, lastname, firstname, id, keep_in_output = keep_remove, extras) |> 
  distinct()

```


## Delete List

```{r}
# delete_list_permanent = c('1 $ New Freezer Donation','1 $ $ for green bags donation','1 $ Food for Ferals Donation','1 $ Food For FS Cats Donation','1 $ Food Pantry Donation','1 $ Freezer Repair Donation','1 $ Paper for Paper - Donation','1 $ Paper for Plastic Donation','1 Each Extra Credit')

delete_list_permanent = sh_delete$item

delete_list_items = df_long_def |> 
  filter(item %in% delete_list_permanent) |> 
  group_by(item) |> 
  summarise(Count = n())

delete_list_items

# delete_list_plants = sh_plants$item

delete_plants = df_long_def |> 
  filter(str_detect(item, 'Pot Plant')) |> 
  # filter(item %in% delete_list_plants) |> 
  group_by(item) |> 
  summarise(Count = n())

delete_plants

delete_no_share = df_long_def |> 
  inner_join(df_long_def |> 
               filter(item %in% order_only_list
                      ) |> 
               select(id) |> 
               distinct()
             , by = c('id')
             ) |> 
  filter(rank == 3) |> 
  group_by(id) |> 
  mutate(rank_v = rank(row_number()),
         rows= max(rank_v)
         ) |>
  ungroup() |> 
  filter(rows == 1) |> 
  select(id) |> 
  distinct()

df_long_def |> 
  filter(id %in% delete_no_share$id) |> 
  select(group_name, description, time, lastname, firstname, item) |> 
  distinct()

df_long_del = df_long_def |> 
  filter(!item %in% delete_list_permanent) |> 
  filter(!id %in% delete_no_share$id) |> 
  filter(!item %in% delete_plants$item)

df_long_del |> head(20)

```

## Plant Print Out

```{r}
plant_output = df_long_def |> 
  filter(item %in% delete_plants$item) |>
  select(group_name, lastname, firstname, item, quantity)

plant_output

wb_p <- createWorkbook(title = 'PotPlant_File')
addWorksheet(wb_p, "sheet1")
writeData(wb_p, "sheet1", plant_output)

saveWorkbook(wb_p, paste0('PotPlant_File_',date,'.xlsx'), overwrite = TRUE)

```


## Optimize orders to two columns

```{r}
optimize_columns = function(data, max_rows) {
  opt_group = data |> 
    ungroup() |> 
    filter(rank >= 0) |> 
    group_by(group_name, description, time, lastname, firstname, id) |> 
    summarise(n = n()) |>  
    ungroup() |> 
    arrange(group_name, description, time, lastname, firstname, desc(n))
  
  group_names = data |>  
    ungroup() |> 
    select(group_name) |> 
    distinct()
  
  column1 = as.data.frame(NULL)
  column2 = as.data.frame(NULL)
  row_max = max_rows - 1 ##one minus the max amount of rows per sheet in print process
  g_name = NULL
  
  
  for (g in 1:dim(group_names)[1]) {
    g_name = group_names$group_name[g]
    opt_grouped = opt_group |> 
      filter(group_name == g_name)
    page = 1
    c1_rows = 0
    c2_rows = 0
    c1_cust = 0
    c2_cust = 0
    name = NA
    for (i in 1:dim(opt_grouped)[1]) {
      name = opt_grouped[i,]
      if (dim(column1)[1] == 0 & dim(column2)[1] == 0 & i == 1) {
        column1 = column1 %>% 
          rbind(opt_grouped[i,] %>% 
                  mutate(page_n = page
                         )
                )
        c1_rows = column1$n[dim(column1)[1]]
        c1_cust = 1
      } else {
        if (floor((opt_grouped$n[i] + c1_rows)/row_max) > 0 & floor((opt_grouped$n[i] + c2_rows)/row_max) > 0) {
          page = page+1
          column1 = column1 %>% 
            rbind(opt_grouped[i,] %>% 
                  mutate(page_n = page
                         )
                )
          c1_rows = column1$n[dim(column1)[1]]
          c2_rows = 0
          c1_cust = 1
          c2_cust = 0
        } else if (floor((opt_grouped$n[i] + c1_rows)/row_max) > 0 & floor((opt_grouped$n[i] + c2_rows)/row_max) == 0) {
          column2 = column2 %>% 
            rbind(opt_grouped[i,] %>% 
                  mutate(page_n = page
                         )
                )
          c2_rows = c2_rows + column2$n[dim(column2)[1]]
          c2_cust = c2_cust + 1
        }  else if (floor((opt_grouped$n[i] + c1_rows)/row_max) == 0 & floor((opt_grouped$n[i] + c2_rows)/row_max) > 0) {
          column1 = column1 %>%
            rbind(opt_grouped[i,] %>%
                  mutate(page_n = page
                         )
                )
          c1_rows = c1_rows + column1$n[dim(column1)[1]]
          c1_cust = c1_cust + 1
        } else if (c1_cust > c2_cust) {
          column2 = column2 %>% 
            rbind(opt_grouped[i,] %>% 
                  mutate(page_n = page
                         )
                )
          c2_rows = c2_rows + column2$n[dim(column2)[1]]
          c2_cust = c2_cust + 1
        } else {
          column1 = column1 %>% 
            rbind(opt_grouped[i,] %>% 
                  mutate(page_n = page
                         )
                )
          c1_rows = c1_rows + column1$n[dim(column1)[1]]
          c1_cust = c1_cust + 1
        }
      }
      # print(opt_grouped$n[i])
    }
  }
  # }
  # 
  # debug(test)
  
  group_name_additions_c1 = data %>% 
    ungroup() |> 
    filter(rank < 0) |> 
    mutate(n = 1) |> 
    select(group_name, description, time, lastname, firstname, id, n) |> 
    left_join(column1 |> 
                select(group_name, page_n) |> 
                distinct()
              , by = c('group_name')
              ) |> 
    rbind(column1) |> 
    arrange(group_name, page_n, description, time, lastname, firstname, desc(n))
  
  group_name_additions_c2 = data %>% 
    ungroup() |> 
    filter(rank < 0) |> 
    mutate(n = 1) |> 
    select(group_name, description, time, lastname, firstname, id, n) |> 
    left_join(column2 |> 
                select(group_name, page_n) |> 
                distinct()
              , by = c('group_name')
              ) |> 
    rbind(column2) |> 
    arrange(group_name, page_n, description, time, lastname, firstname, desc(n))
    
  row_df = data.frame(row_n = 0:row_max+1)
  print_full = column1 |> 
    select(group_name, page_n) |> 
    distinct() |> 
    full_join(row_df, by = character()
              )
  
  column1_w_groups = group_name_additions_c1 |> 
    select(id, n, page_n, group_name_col = group_name) |> 
    left_join(data |> 
                ungroup() |> 
                filter(rank >= 0)
              , by = c('id')
              ) |> 
    mutate(item = ifelse(is.na(rank), group_name_col, item),
           group_name = ifelse(is.na(rank), group_name_col, group_name),
           rank = ifelse(is.na(rank), -1, rank)
           ) |> 
    select(-group_name_col) |> 
    group_by(group_name, page_n) |> 
    mutate(row_n = rank(row_number()))
  
  column2_w_groups = group_name_additions_c2 |> 
    select(id, n, page_n, group_name_col = group_name) |> 
    left_join(data |> 
                ungroup() |> 
                filter(rank >= 0)
              , by = c('id')
              ) |> 
    mutate(item = ifelse(is.na(rank), group_name_col, item),
           group_name = ifelse(is.na(rank), group_name_col, group_name),
           rank = ifelse(is.na(rank), -1, rank)
           ) |> 
    select(-group_name_col) |> 
    group_by(group_name, page_n) |> 
    mutate(row_n = rank(row_number()))
  
  stopifnot(column1_w_groups |> 
      filter(row_n > row_max+1) |> 
      summarise(n=n()) |> 
      pull() == 0)
  
  stopifnot(column2_w_groups |> 
      filter(row_n > row_max+1) |> 
      summarise(n=n()) |> 
      pull() == 0)
  
  column1_print = print_full |> 
    left_join(column1_w_groups
              , by = c('group_name', 'page_n', 'row_n')
    )
  
  column2_print = print_full |> 
    left_join(column2_w_groups
              , by = c('group_name', 'page_n', 'row_n')
    )
  
  column_print_combined = column1_print |> 
    mutate(column = 1) |> 
    rbind(column2_print |> 
            mutate(column = 2)
          )
  
  return(column_print_combined)
}

column_print_comb_excel = optimize_columns(df_long_del, 46)
column_print_comb_openo = optimize_columns(df_long_del, 46) # Have to make all row heights = 0.22"
# column_print_comb_sheets = optimize_columns(df_long_del, 47)

```


## adding in symbols or emojis

```{r}
# test = data.frame(emoji::emoji_name)
# test = test |> rownames_to_column()
# colnames(test) = c('name', 'emoji')
# 
# keywords <- emo::ji_keyword
# emojis <- purrr::map_chr(keywords, function(x) paste0(x, collapse = ","))
# test2 = data.frame(keywords = names(emojis)
#                    , emojis)
# colnames(test2) = c('keyword', 'name_list')
# test2_long = test2 |>
#   mutate(name = strsplit(as.character(name_list), ",")) |>
#   unnest(name) |>
#   select(keyword, name) |>
#   distinct()
# 
# test_comb = test |>
#   left_join(test2_long
#             , by = c('name')
#             ) |>
#   arrange(name, keyword) |>
#   group_by(name, emoji) |>
#   mutate(keyword_list = paste0(keyword, collapse = ",")) |>
#   ungroup() |>
#   select(-keyword) |>
#   distinct()
# 
# fs_emoji_df = test_comb |> 
#   filter(str_detect(keyword_list,'beer')
#          | str_detect(keyword_list,'plant')
#          | str_detect(keyword_list,'pizza')
#          | str_detect(keyword_list,'food')
#          | str_detect(keyword_list,'vege')
#          | str_detect(keyword_list,'cow')
#          | str_detect(keyword_list,'chicken')
#          | str_detect(keyword_list,'fish')
#          | str_detect(keyword_list,'shrimp')
#          | str_detect(keyword_list,'cheese')
#            )

# 
# wb_e <- createWorkbook(title = 'emoji.xlsx')
# addWorksheet(wb_e, "sheet1")
# writeData(wb_e, "sheet1", test_comb, colNames = TRUE)
# 
# openXL(wb_e)
# saveWorkbook(wb_e, "emoji.xlsx", overwrite = TRUE)

# df_symbol_inputs = data.frame(match_name = c('equal', 'contains', 'contains')
#                              ,text_name = c('1 Dozen Eggs', 'MILK', 'Chocolate')
#                              ,freeform_text = c(NA, '[***]', NA)
#                              ,emoji_name = c(emo::ji('chicken'), emo::ji('cow'), emo::ji('chocolate'))
#                              )

df_symbol_inputs_milk = data.frame(match_name = c('contains', 'contains', 'contains'
                                                  , 'contains', 'contains', 'contains'
                                                  , 'contains', 'contains', 'contains'
                                                  , 'contains', 'contains', 'contains')
                             ,text_name = c('Milk - 2%','Milk - Chocolate','Milk - Creamline'
                                            , 'Milk - Skim','Milk - Whole', '2% MILK'
                                            , 'Chocolate MILK', 'Creamline MILK', 'Skim MILK'
                                            , 'Whole MILK', 'Whole Milk - o'
                                            , '64 Oz. Heavy Cream')
                             ,freeform_text = c('[*]', '[*]', '[*]', '[*]', '[*]'
                                                , '[*]', '[*]', '[*]', '[*]', '[*]'
                                                , '[*]', '[*]')
                             ,emoji_name = c(emo::ji('cow2'), emo::ji('cow2'), emo::ji('cow2')
                                             , emo::ji('cow2'), emo::ji('cow2'), emo::ji('cow2')
                                             , emo::ji('cow2'), emo::ji('cow2'), emo::ji('cow2')
                                             , emo::ji('cow2'), emo::ji('cow2'), emo::ji('cow2'))
                             )

df_symbol_inputs_pizza = data.frame(match_name = c('contains', 'contains', 'contains'
                                                   , 'contains', 'contains', 'contains'
                                                   , 'contains', 'contains')
                             ,text_name = c('Pizza - Cheese','Pizza - Deluxe'
                                            ,'Pizza - Four Meat','Pizza - Hot Chicken'
                                            ,'Pizza - Pepperoni','Pizza - Sausage Pepperoni'
                                            ,'Pizza - Tomato Basil Garlic','Pizza - Veggie')
                             ,freeform_text = c('[**]', '[**]', '[**]', '[**]'
                                                , '[**]', '[**]', '[**]', '[**]')
                             ,emoji_name = c(emo::ji('pizza'), emo::ji('pizza'), emo::ji('pizza')
                                             , emo::ji('pizza'), emo::ji('pizza'), emo::ji('pizza')
                                             , emo::ji('pizza'), emo::ji('pizza'))
                             )

df_symbol_inputs_other = data.frame(match_name = c('contains', 'contains','contains'
                                                   ,'contains','contains','contains')
                             ,text_name = c('FF Dish - Creole Shrimp & Okra'
                                            , 'Pork - Andouille links','Raw Milk Aged Cheddar'
                                            , 'Pickup Time','Schlafly Beer'
                                            , 'Pre-ordered Plants')
                             ,freeform_text = c('[**]', '[andouille]', '[1]',NA, NA,NA)
                             ,emoji_name = c(emo::ji('fried_shrimp'), NA, emo::ji('cheese')
                                             , emo::ji('clock3'), emo::ji('beer')
                                             , emo::ji('seedling'))
                             )
df_symbol_inputs = df_symbol_inputs_milk |> 
  rbind(df_symbol_inputs_pizza) |> 
  rbind(df_symbol_inputs_other)

symbol_addition = function(item_n, match_n, text_n, ff_n, em_n) {
  ifelse((!is.na(ff_n)) & (!is.na(em_n)),
      ifelse(match_n == 'equal', ifelse(item_n == text_n, paste0(em_n, ff_n), NA),
      ifelse(match_n == 'contains', ifelse(str_detect(item_n, text_n), paste0(em_n, ff_n), NA),
      ifelse(match_n == 'starts with', ifelse(startsWith(item_n, text_n), paste0(em_n, ff_n), NA),
      ifelse(match_n == 'ends with', ifelse(endsWith(item_n, text_n), paste0(em_n, ff_n), NA)
             , NA))))
  ,ifelse((!is.na(ff_n)), 
      ifelse(match_n == 'equal', ifelse(item_n == text_n, paste0(ff_n), NA),
      ifelse(match_n == 'contains', ifelse(str_detect(item_n, text_n), paste0(ff_n), NA),
      ifelse(match_n == 'starts with', ifelse(startsWith(item_n, text_n), paste0(ff_n), NA),
      ifelse(match_n == 'ends with', ifelse(endsWith(item_n, text_n), paste0(ff_n), NA)
             , NA))))
  ,ifelse((!is.na(em_n)) , 
      ifelse(match_n == 'equal', ifelse(item_n == text_n, paste0(em_n), NA),
      ifelse(match_n == 'contains', ifelse(str_detect(item_n, text_n), paste0(em_n), NA),
      ifelse(match_n == 'starts with', ifelse(startsWith(item_n, text_n), paste0(em_n), NA),
      ifelse(match_n == 'ends with', ifelse(endsWith(item_n, text_n), paste0(em_n), NA)
             , NA))))   
  , NA)))
}

# symbol_search_c1 = column1_print |> 
#   select(item) |> 
#   distinct() |> 
#   full_join(df_symbol_inputs
#             , by = character()
#             ) |> 
#   mutate(symbol_text = symbol_addition(item, match_name, text_name, freeform_text, emoji_name)) |> 
#   filter(!is.na(symbol_text)) |> 
#   select(item, symbol_text) |> 
#   arrange(item, symbol_text) |> 
#   group_by(item) |> 
#   mutate(symbol_text = paste0(symbol_text, collapse = "")) |> 
#   ungroup() |> 
#   distinct()
# 
# df_long_symbol_c1 = column1_print |> 
#   left_join(symbol_search_c1
#             , by = c('item')
#             ) |> 
#   mutate(quantity = ifelse(is.na(quantity), '', as.character(quantity))
#            , item = ifelse(is.na(item), '', item)
#            , item_symbol = ifelse(quantity == '', item, paste0(quantity,'x',item))
#            , qty_symbol = ifelse(quantity > 1, emo::ji('plus'), '')
#            , item_symbol = ifelse(is.na(symbol_text)
#                                   , paste0(qty_symbol, item_symbol)
#                                   , paste0(qty_symbol, symbol_text, item_symbol))
#          )
# 
# symbol_search_c2 = column2_print |> 
#   select(item) |> 
#   distinct() |> 
#   full_join(df_symbol_inputs
#             , by = character()
#             ) |> 
#   mutate(symbol_text = symbol_addition(item, match_name, text_name, freeform_text, emoji_name)) |> 
#   filter(!is.na(symbol_text)) |> 
#   select(item, symbol_text) |> 
#   arrange(item, symbol_text) |> 
#   group_by(item) |> 
#   mutate(symbol_text = paste0(symbol_text, collapse = "")) |> 
#   ungroup() |> 
#   distinct()
# 
# df_long_symbol_c2 = column2_print |> 
#   left_join(symbol_search_c2
#             , by = c('item')
#             ) |> 
#   mutate(quantity = ifelse(is.na(quantity), '', as.character(quantity))
#            , item = ifelse(is.na(item), '', item)
#            , item_symbol = ifelse(quantity == '', item, paste0(quantity,'x',item))
#            , qty_symbol = ifelse(quantity > 1, emo::ji('plus'), '')
#            , item_symbol = ifelse(is.na(symbol_text)
#                                   , paste0(qty_symbol, item_symbol)
#                                   , paste0(qty_symbol, symbol_text, item_symbol))
#          )

add_item_styling = function(data) {
  symbol_search = data |> 
    select(item) |> 
    distinct() |> 
    full_join(df_symbol_inputs
              , by = character()
              ) |> 
    mutate(symbol_text = symbol_addition(item, match_name, text_name, freeform_text, emoji_name)) |> 
    filter(!is.na(symbol_text)) |> 
    select(item, symbol_text) |> 
    arrange(item, symbol_text) |> 
    group_by(item) |> 
    mutate(symbol_text = paste0(symbol_text, collapse = "")) |> 
    ungroup() |> 
    distinct()
  
  df_long_symbol = data |> 
    left_join(symbol_search
              , by = c('item')
              ) |> 
    mutate(quantity = ifelse(is.na(quantity), '', as.character(quantity))
             , item = ifelse(is.na(item), '', item)
             , item_symbol = ifelse(quantity == '', item, paste0(quantity,'x',item))
             , qty_symbol = ifelse(quantity > 1, emo::ji('plus'), '')
             , item_symbol = ifelse(is.na(symbol_text)
                                    , paste0(qty_symbol, item_symbol)
                                    , paste0(qty_symbol, symbol_text, item_symbol))
           )
  return(df_long_symbol)
}

df_long_symbol_excel = add_item_styling(column_print_comb_excel)
df_long_symbol_openo = add_item_styling(column_print_comb_openo)
# df_long_symbol_sheets = add_item_styling(column_print_comb_sheets)

```

## PDF attempt

Still having issue with emojis in output.
Potential next attempt might be using reticulate along with Python to get result necessary

```{r}
pdf("multipage_test.pdf")

print_pages = df_long_symbol_excel |> select(group_name, page_n) |> distinct()

for (x in 1:dim(print_pages)[1]) {
  v = df_long_symbol_excel |>
    filter(group_name == print_pages[x,]$group_name 
           & page_n == print_pages[x,]$page_n
           & column == 1) |>
    select(item_symbol) |> 
    cbind(df_long_symbol_excel |>
    filter(group_name == print_pages[x,]$group_name 
           & page_n == print_pages[x,]$page_n
           & column == 2) |>
    select(item_symbol))
  grid::grid.newpage()
  gridExtra::grid.table(v, rows = NULL)
}

dev.off
```

## Highlight Share / customer names (via Excel)

```{r}
## Create function to do color or text change based on search criteria in item


workbook_created = function(data, width, height) {
  df_long_sh_color_c1 = data |> 
    filter(column == 1) |> 
    left_join(sh_shares_shrt
              , by = c('group_name')
              ) |> 
    mutate(highlight_color_hex = ifelse(rank <= 0, highlight_color_hex, NA))
  
  df_long_sh_color_c2 = data |> 
    filter(column == 2) |> 
    left_join(sh_shares_shrt
              , by = c('group_name')
              ) |> 
    mutate(highlight_color_hex = ifelse(rank <= 0, highlight_color_hex, NA))
  
  write_df = df_long_sh_color_c1 |>
    mutate(item_symbol = ifelse(rank == -1
                               , paste0(item_symbol, ' (',week, ' - ', date,')')
                               , item_symbol)
           ) |> 
    select(item_1 = item_symbol) |>
    cbind(
      df_long_sh_color_c2 |>
        mutate(item_symbol = ifelse(rank == -1
                               , paste0(item_symbol, ' (',week, ' - ', date,')')
                               , item_symbol)
           ) |> 
        select(item_2 = item_symbol)
    )
  
  wb <- createWorkbook(title = 'TestFile')
  addWorksheet(wb, "testing")
  writeData(wb, "testing", write_df, colNames = FALSE)
  
  setColWidths(wb, "testing", cols = 1:2, widths = width)
  setRowHeights(wb, "testing", rows = (dim(data)[1]/2), heights = height)
  modifyBaseFont(wb, fontSize = 12, fontColour = "black", fontName = "Calibri")
  
  ## Coloring each Group and Member names based on Google Sheet 
  
  #### Column 1
  test_color_c1 = df_long_sh_color_c1 |> 
    mutate(ss_cell = row_number()) |> 
    filter(!is.na(highlight_color_hex)) 
  
  for (i in (test_color_c1 |> select(highlight_color_hex) |> distinct() |> pull())) {
    print(i)
    bhfill_style <- createStyle(bgFill = i, textDecoration = "bold")
  
    for (j in (test_color_c1 |> filter(highlight_color_hex == i) |> select(ss_cell) |> distinct() |> pull())) {
      conditionalFormatting(wb, "testing", rule = "!=0", cols = 1, rows = j, style = bhfill_style)
      addStyle(wb, "testing", cols = 1, rows = j, style = createStyle(halign = "center"))
    }
  
  }
  
  #### Column 2
  test_color_c2 = df_long_sh_color_c2 |> 
    mutate(ss_cell = row_number()) |> 
    filter(!is.na(highlight_color_hex)) 
  
  for (i in (test_color_c2 |> select(highlight_color_hex) |> distinct() |> pull())) {
    print(i)
    bhfill_style <- createStyle(bgFill = i, textDecoration = "bold")
  
    for (j in (test_color_c2 |> filter(highlight_color_hex == i) |> select(ss_cell) |> distinct() |> pull())) {
      conditionalFormatting(wb, "testing", rule = "!=0", cols = 2, rows = j, style = bhfill_style)
      addStyle(wb, "testing", cols = 2, rows = j, style = createStyle(halign = "center"))
    }
  
  }
  
  ## Bold each item if its in the Standard Item List for that group
  
  bold_stndrd_item_c1 = df_long_sh_color_c1 |> 
    mutate(ss_cell = row_number()) |> 
    filter(!is.na(standard_item)) 
  
  for (j in (bold_stndrd_item_c1 |> select(ss_cell) |> distinct() |> pull())) {
    bhfill_style <- createStyle(textDecoration = "bold")
    conditionalFormatting(wb, "testing", rule = "!=0", cols = 1, rows = j, style = bhfill_style)
    }
  
  bold_stndrd_item_c2 = df_long_sh_color_c2 |> 
    mutate(ss_cell = row_number()) |> 
    filter(!is.na(standard_item)) 
  
  for (j in (bold_stndrd_item_c2 |> select(ss_cell) |> distinct() |> pull())) {
    bhfill_style <- createStyle(textDecoration = "bold")
    conditionalFormatting(wb, "testing", rule = "!=0", cols = 2, rows = j, style = bhfill_style)
  }
  
  
  style_xlsx = function(wb_n, sheet, col_n, match, text, colorhex, text_dec_name) {
    if (!is.na(colorhex) & !is.na(text_dec_name)) {  #HIGHLIGHT BACKGROUND AND DECORATE TEXT
      if (match == 'equal') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(df_long_sh_color$item == text)
             , style = createStyle(fgFill = colorhex
                                   ,textDecoration = text_dec_name)
             )
      } else if (match == 'contains') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(str_detect(df_long_sh_color$item, pattern = text))
             , style = createStyle(fgFill = colorhex
                                   ,textDecoration = text_dec_name)
             )
      } else if (match == 'starts with') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(startsWith(df_long_sh_color$item, text))
             , style = createStyle(fgFill = colorhex
                                   ,textDecoration = text_dec_name)
             )
      } else if (match == 'ends with') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(endsWith(df_long_sh_color$item, text))
             , style = createStyle(fgFill = colorhex
                                   ,textDecoration = text_dec_name)
             )
      } else {
        print('valid match type not determined')
      }
    } else if (!is.na(colorhex)) {    #HIGHLIGHT BACKGROUND ONLY
      if (match == 'equal') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(df_long_sh_color$item == text)
             , style = createStyle(fgFill = colorhex)
             )
      } else if (match == 'contains') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(str_detect(df_long_sh_color$item, pattern = text))
             , style = createStyle(fgFill = colorhex)
             )
      } else if (match == 'starts with') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(startsWith(df_long_sh_color$item, text))
             , style = createStyle(fgFill = colorhex)
             )
      } else if (match == 'ends with') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(endsWith(df_long_sh_color$item, text))
             , style = createStyle(fgFill = colorhex)
             )
      } else {
        print('valid match type not determined')
      }
    } else if (!is.na(text_dec_name)) {   #DECORATE TEXT ONLY
      if (match == 'equal') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(df_long_sh_color$item == text)
             , style = createStyle(textDecoration = text_dec_name)
             )
      } else if (match == 'contains') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(str_detect(df_long_sh_color$item, pattern = text))
             , style = createStyle(textDecoration = text_dec_name)
             )
      } else if (match == 'starts with') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(startsWith(df_long_sh_color$item, text))
             , style = createStyle(textDecoration = text_dec_name)
             )
      } else if (match == 'ends with') {
        addStyle(wb_n, sheet
             , cols = col_n
             , rows = which(endsWith(df_long_sh_color$item, text))
             , style = createStyle(textDecoration = text_dec_name)
             )
      } else {
        print('valid match type not determined')
      }
    } else {
      print('Need to selet a color or text format type')
    }
    
  }
    
  
  
  df_long_sh_color = df_long_sh_color_c1
  # style_xlsx(wb, "testing", 1, 'equal', "1 Dozen Eggs", '#ffff00', NA)
  # style_xlsx(wb, "testing", 1, 'starts with', "64 Oz. Milk - Whole", '#00ffff', NA)
  # style_xlsx(wb, "testing", 1, 'ends with', "Green Curly", '#00ff00', NA)
  
  # style_xlsx(wb, "testing", 1, 'contains', "Pickup Time", '#efefef', 'bold')
  # style_xlsx(wb, "testing", 1, 'contains', "Pickup Time", NA, 'bold')
  style_xlsx(wb, "testing", 1, 'equal', "STANDARD SHARE ITEMS", NA, 'bold')
  style_xlsx(wb, "testing", 1, 'contains', "Pickup Time", NA, 'italic')
  
  df_long_sh_color = df_long_sh_color_c2
  # style_xlsx(wb, "testing", 2, 'equal', "1 Dozen Eggs", '#ffff00', NA)
  # style_xlsx(wb, "testing", 2, 'starts with', "64 Oz. Milk - Whole", '#00ffff', NA)
  # style_xlsx(wb, "testing", 2, 'ends with', "Green Curly", '#00ff00', NA)
  
  # style_xlsx(wb, "testing", 2, 'contains', "Pickup Time", '#efefef', 'bold')
  # style_xlsx(wb, "testing", 2, 'contains', "Pickup Time", NA, 'bold')
  
  style_xlsx(wb, "testing", 2, 'equal', "STANDARD SHARE ITEMS", NA, 'bold')
  style_xlsx(wb, "testing", 2, 'contains', "Pickup Time", NA, 'italic')
  
  # openXL(wb)
  return(wb)
}

wb_excel = workbook_created(df_long_symbol_excel, 39, 24)
wb_openo = workbook_created(df_long_symbol_openo, 39, 30)
# wb_sheets = workbook_created(df_long_symbol_sheets, 34)


saveWorkbook(wb_excel, paste0('print_excel_',date,'.xlsx'), overwrite = TRUE)
saveWorkbook(wb_openo, paste0('print_openo_',date,'.xlsx'), overwrite = TRUE)
# saveWorkbook(wb_sheets, paste0('print_sheets_',date,'.xlsx'), overwrite = TRUE)
# saveWorkbook(wb, "TestFile.xlsx", overwrite = TRUE)

### PDF and PNG attempts with little room for success
# library(gridExtra) 
# pdf("test.pdf", height=11, width=10, onefile=FALSE)
# grid.table(write_df)
# dev.off()
# 
# png("test.png", height = 1200, width = 600)
# grid.table(write_df)
# dev.off()

# ## Uploading file to Googledrive looks VERY promising
# ### Google Sheets does not print emojis. they need to be actual images. 
# ### Google Sheets does not print the same amount of rows each time. its inconsistent in printing
# gs_file <- drive_upload(paste0(getwd(),'/','print_sheets_',date,'.xlsx'), type = "spreadsheet")
# # drive_browse(gs_file)
# gs_move <- drive_mv(gs_file, path = "check_in_list_drop_location/", overwrite = TRUE)
# sheet_resize(gs_move, nrow = dim(df_long_symbol_sheets)[1]/2, ncol = 2, exact = TRUE)
# range_autofit(gs_move, dimension = 'rows')
# drive_browse(gs_move)


##Another option to explore
# library(readODS)
# write_ods(iris, "iris.ods")
```

## Member Count - End

```{r}
member_end = df_long_del |> 
  filter(rank >= 0) |> 
  select(group_name, firstname, lastname) |> 
  distinct() |> 
  group_by(group_name) |> 
  summarise(n_end = n())

member_start |> 
  full_join(member_end
            , by = c('group_name')) |> 
  mutate(difference = n_start - n_end)

```

